Visualization and analysis of probability distributions of large temporal data

### 2021-11-15 Rmd/02-gravitas.Rmd
ch: to ch-
paper-gracsr update

# Visualizing probability distributions across bivariate cyclic temporal granularities {#ch:gravitas}

@@

\noindent In the Mayan calendar (Table \@ref(tab:tab-mayan)), kin-of-tun or kin-of-baktun are examples of multiple-order-up granularities and single-order-up granularities are kin-of-uinal, uinal-of-tun etc.

>>>>

# Visualizing probability distributions across bivariate cyclic temporal granularities {#ch-gravitas}

@@

\noindent In the Mayan calendar (Table \@ref{tab:tab-mayan}), kin-of-tun or kin-of-baktun are examples of multiple-order-up granularities and single-order-up granularities are kin-of-uinal, uinal-of-tun etc.
